\cvsection{Experience}
\begin{cventries}
\cventry
  {Undergraduate Research}
  {Informatics Initiative}
  {Iowa City, IA}
  {Feb. 2017 - July 2017}
  {
    \begin{cvitems}
      \item {Coauthored \textit{Understanding the Effect of the Travel Ban on Immigration Tweets in the United States}, extending a class project, by working with Political Scientists, Geographers, and a Professor.}
      \item {Unearthed hidden geographic trends in Twitter data by analyzing 500Gb of tweets from 97 languages in Python and ArcGIS.}
      \item {Expanded community engagement via leading a new Data Science summer workshop.}
    \end{cvitems}
  }
  \cventry
    {Undergraduate Research}
    {IDEA Lab}
    {Iowa City, IA}
    {Sep. 2016 - Feb. 2017}
    {
      \begin{cvitems}
        \item{Implemented performant emotion and attention classifiers from prior computer vision literature (OpenCV, Raspberry Pi).}
        \item {Designed and developed a physical anomaly predictor using athlete's gyroscopic data (Scikit-Learn). }
      \end{cvitems}
    }
  \cventry
    {Data Journalist}
    {Daily Iowan}
    {Iowa City, IA}
    {Sep. 2016 - Dec. 2016}
    {
      \begin{cvitems}
        \item {Co-founded the Daily Iowan Data Journalism Team, by integrating quantitative information, journalists, and the school's newspaper \textit{The Daily Iowan}.}
        \item {Published 4 monthly print and web projects to communicate data stories, by collaborating with reporters on choice editorials (D3.js, Illustrator).}
      \end{cvitems}
    }
  \cventry
    {Data Visualization Intern}
    {ACT}
    {Iowa City, IA}
    {Jun. 2016 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Synthesized recommendations by analyzing 11 datasets from 4 open and closed sources (Python, Jupyter Notebooks). }
        \item {Increased user engagement by scaling an interactive web visualization platform using predictive models and D3.js.}
      \end{cvitems}
    }
  \cventry
    {Data Analyst Intern}
    {ACT}
    {Iowa City, IA}
    {Jun. 2015 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Identified areas of growth for ACT, by analyzing 2 decades of survey data and performance metrics.}
        \item {Communicated insights to stake holders, by creating interactive Tableau dashboards and static reports, leading to a company decision involving 100 people.}
      \end{cvitems}
    }
  \cventry
    {Desktop Support Analyst}
    {College of Public Health}
    {Iowa City, IA}
    {July. 2013 - Ongoing}
    {
      \begin{cvitems}
        \item {Diagnosed and resolved hardware, software problems. Worked with users to extract critical information and provide timely support. }
      \end{cvitems}
    }
\end{cventries}
